Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-12-12 src/tex/ms.tex
change colors of plots

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
%        \includegraphics[width=\hsize]{figures/hz_nuv_evo.bak.png}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} (right) as a function of host star mass.
        Scatter points show age and host star mass of the transiting planets in the synthetic planet sample; crosses denote the estimated \gls{NUV} values in \citet{Richey-Yowell2019}. % with \gls{EEC} highlighted in green.
        We show three evolutionary tracks for a threshold flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$ that occupy the \gls{HZ} (green sections) and exceed the threshold \gls{NUV} flux (blue sections) at different times.
        Where these sections overlap (orange rectangles), the requirements for abiogenesis are met and we assign a biosignature detection with probability $f_\mathrm{life}$.
        Planet~1 is an \gls{EEC} orbiting a K~dwarf that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

\begin{figure*}
    \script{surveys_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/surveys_FGKM}
        \caption{
        Simulated transit surveys targeting FGK and M~stars.\\
        Top: Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
        In the FGK sample, all \glspl{EEC} and all inhabited planets orbit K~dwarfs.
        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.\\
        Center: Distribution of inferred maximum past \gls{NUV} flux in transit surveys targeting \glspl{EEC} around FGK and M~stars, respectively. The best-fit beta distributions (gray) correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}. Green areas show inhabited planets for an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a generic threshold \gls{NUV} flux $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.\\
        Bottom: Recovered biosignature detections and non-detections of simulated transit surveys. The dashed line denotes $F_\mathrm{NUV, min}$.}
        \label{fig:surveys_FGKM}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
%        \includegraphics[width=\hsize]{figures/hz_nuv_evo.bak.png}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} (right) as a function of host star mass.
        Scatter points show age and host star mass of the transiting planets in the synthetic planet sample; crosses denote the estimated \gls{NUV} values in \citet{Richey-Yowell2019}. % with \gls{EEC} highlighted in green.
        We show three evolutionary tracks for a threshold flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$ that occupy the \gls{HZ} (yellow sections) and exceed the threshold \gls{NUV} flux (red sections) at different times.
        Where these sections overlap (white rectangles), the requirements for abiogenesis are met and we assign a biosignature detection with probability $f_\mathrm{life}$.
        Planet~1 is an \gls{EEC} orbiting a K~dwarf that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

\begin{figure*}
    \script{surveys_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/surveys_FGKM}
        \caption{
        Simulated transit surveys targeting FGK and M~stars.\\
        Top: Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
        In the FGK sample, all \glspl{EEC} and all inhabited planets orbit K~dwarfs.
        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.\\
        Center: Distribution of inferred maximum past \gls{NUV} flux in transit surveys targeting \glspl{EEC} around FGK and M~stars, respectively. The best-fit beta distributions correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}. Red areas show inhabited planets for an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a generic threshold \gls{NUV} flux $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.\\
        Bottom: Recovered biosignature detections and non-detections of simulated transit surveys. The dashed line denotes $F_\mathrm{NUV, min}$.}
        \label{fig:surveys_FGKM}
    \end{centering}
\end{figure*}
